Andres Karjus

### 2018-10-06 index.Rmd
postprint

- Out now in Language Dynamics and Change: Karjus & Ehala 2018, Testing an agent based model of language choice on sociolinguistic survey data | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [PDF](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): representative sample of 1000 respondents from Estonia, 200 questions on language attitudes and use

@@

* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [PDF](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | <a href="karjus_quantifying_2018.bib" target="_blank">bib</a> | [code](https://github.com/andreskarjus/topical_cultural_advection_model) | recipient of the Edinburgh PPLS [Gray postgraduate publication prize](https://www.ed.ac.uk/ppls/philosophy/current/postgraduate/fees-and-funding/ppls-gray-postgraduate-publication-prize)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.

>>>>

- Out now in Language Dynamics and Change: Karjus & Ehala 2018, Testing an agent based model of language choice on sociolinguistic survey data | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [postprint pdf](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): representative sample of 1000 respondents from Estonia, 200 questions on language attitudes and use

@@

* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [Online at Brill](https://doi.org/10.1163/22105832-00802004) | [postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Quantifying the dynamics of topical fluctuations in language. | [arXiv preprint](https://arxiv.org/abs/1806.00699) | <a href="karjus_quantifying_2018.bib" target="_blank">bib</a> | [code](https://github.com/andreskarjus/topical_cultural_advection_model) | recipient of the Edinburgh PPLS [Gray postgraduate publication prize](https://www.ed.ac.uk/ppls/philosophy/current/postgraduate/fees-and-funding/ppls-gray-postgraduate-publication-prize)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [online version](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
*	Andres Karjus, 2015. Through the Spyglass of Synchrony: Grammaticalization of the Exterior Space in the Eastern Circum-Baltic. In: Hilpert, Martin, Östman, Jan-Ola, Mertzlufft, Christine, Rießler, Michael, Duke, Janet (eds.), Advances in Nordic Linguistics. De Gruyter Mouton.
| [google books](https://books.google.ee/books?id=BPheCAAAQBAJ)
*	Andres Karjus (editor), 2013. Areal linguistics, Grammar and Contacts. Special issue of the Journal of Estonian and Finno-Ugric Linguistics, 4-2. Tartu: University of Tartu Press. 
| [open access](http://jeful.ut.ee/index.php/JEFUL/issue/view/2013.4.2)
* Petar Kehayov, Eva Saar, Miina Norvik, Andres Karjus, 2013. Hääbuva kesklüüdi murde jälgedel suvel 2012 [On the footsteps of vanishing Central Lude in the summer of 2012]. Yearbook of the Estonian Mother Tongue Society, Vol. 58. | [open access](http://www.kirj.ee/public/ESA/2012/esa_58-2012-58-101.indd.pdf)
*	Andres Karjus, 2012. Outdoors on the Shores of the Baltic: Gradience in the Grammaticalization of the Exterior-Region. Journal of Estonian and Finno-Ugric Linguistics 3-1, pp. 209-226.
